---
title: "Name of the Learnr Tutorial"
author: "[Peter Baumgartner](https://github.com/petzi53)"
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
bibliography: "www/references.bib"
link-citations: true
editor_options:
  markdown:
    wrap: 72
    references: 
      location: block
    canonical: true

output: 
    learnr::tutorial:
        progressive: true
        allow_skip: true
        theme: "cerulean"
        css: "css/style.css"
runtime: shiny_prerendered
---

```{r setup, echo=F, message=F, warning=F, include=F}
library(tidyverse)
library(learnr)
library(gradethis)
library(usethis)

```

## Standard examples

### No retry

The next example works because `allow_retry = FALSE` (default value).
There is no possibility give correct feedback in every case if
`allow_retry = TRUE`.

```{r where-am-i}
question("Where are you right now? (select ALL that apply)",
  answer("Planet Earth", correct = TRUE),
  answer("Pluto"),
  answer("At a computing device", correct = TRUE),
  answer("In the Milky Way", correct = TRUE),
  incorrect = "Incorrect. You're on Earth, in the Milky Way, at a computer."
)
```

### No nuanced feedback

The following example does not allow a partly correct answers, e.g.
answering three of four topping correctly. Besides it gives wrong
feedback if correct and wrong topics are chosen.

```{r checkbox-example}
question(
  "Select all the toppings that belong on a Margherita Pizza:",
  answer("tomato", correct = TRUE),
  answer("mozzarella", correct = TRUE),
  answer("basil", correct = TRUE),
  answer("extra virgin olive oil", correct = TRUE),
  answer("pepperoni", message = "Great topping! ... just not on a Margherita Pizza"),
  answer("onions"),
  answer("bacon"),
  answer("spinach"),
  random_answer_order = FALSE,
  allow_retry = TRUE,
  try_again = "Be sure to select all toppings!"
)
```

You cannot save the feedback by replacing the try_again to "Be sure to
select only the correct toppings!" or other sentences. In some
combination it will turn out wrong.

## Interpretation in context

Taken from [Regression modeling: 4 - Interpreting regression
models](https://openintro.shinyapps.io/ims-03-model-04/#section-your-turn)
and adapted to Multiple Choice question

A politician interpreting the relationship between poverty rates and
high school graduation rates implores his constituents:

> If we can lower the poverty rate by 59%, we'll double the high school
> graduate rate in our county (i.e. raise it by 100%).

```{r mc2}
question("Which of the following mistakes in interpretation has the politician made?",
  answer("Implying that the regression model establishes a cause-and-effect relationship.", correct = TRUE),
  answer("Switching the role of the response and explanatory variables.", correct = TRUE),
  answer("Confusing percentage change with percentage point change.", correct = TRUE),
  answer("None of the above.", correct = FALSE),
  incorrect = "Only partly correct: The politician has made more mistakes in interpreting the relationship.",
  allow_retry = TRUE
)
```

### Another version

This version has a additional incorrect answer options

```{r mc2a}
question("Which of the following mistakes has the politician made?",
  answer("Implying that the regression model establishes a cause-and-effect relationship.", correct = TRUE),
  answer("The politician does not interpret, he just reports the facts.", correct = FALSE),
  answer("Switching the role of the response and explanatory variables.", correct = TRUE),
  answer("Confusing percentage change with percentage point change.", correct = TRUE),
  answer("None of the above.", correct = FALSE),
  incorrect = "Only partly correct: The politician has made more mistakes in interpreting the relationship.",
  allow_retry = TRUE
)
```

## Misc Tests

```{r checkbox, echo = FALSE}
question(
  "Select all the toppings that belong on a Margherita Pizza:",
  answer("tomato", correct = TRUE,   message = "Partly correct"),
  answer("mozzarella", correct = TRUE),
  answer("basil", correct = TRUE),
  answer("extra virgin olive oil", correct = TRUE),
  answer("pepperoni", message = "Great topping! ... just not on a Margherita Pizza"),
  answer("onions"),
  answer("bacon"),
  answer("spinach"),
  try_again = "Be sure to select all toppings!",

  random_answer_order = FALSE,
  allow_retry = TRUE

)
```

```{r radio, echo = FALSE}
question(
  "Is this a good question?",
  answer("yes", correct = TRUE),
  answer("no", message = 'This is a good question.'),
  allow_retry = TRUE,
  try_again = "Be sure to select all toppings!"
)
```

```{r options, echo = FALSE}
question(
  "How many parameters are supplied in this question?",
  answer("1", message = "Really?"),
  answer("2"),
  answer("3"),
  answer("15", correct = TRUE, message = "Custom message here."),
  type = "learnr_text",
  correct = "Question is correct!",
  message = "Reminder to do something after answering the question...",
  post_message = "Message to be displayed after the correct answer is found",
  submit_button = "Submit Answer Here!",
  try_again_button = "Try Again Here!",
  allow_retry = TRUE,
  random_answer_order = TRUE,
  options = list(
    placeholder = "The answer is '15'",
    trim = TRUE
  )
)
```

```{r format-question}
ex_question <- question("What number is the letter A in the alphabet?",
  answer("8"),
  answer("14"),
  answer("1", correct = TRUE),
  answer("23"),
  incorrect = "See [here](https://en.wikipedia.org/wiki/English_alphabet) and try again.",
  allow_retry = TRUE
)

```
